On consistency scores in text data with an implementation in R

### 2021-01-08 outputs/documents/paper_ngrams.Rmd
corrected model outputs

  # Create ngrams from the tokens
  toks_ngram <- 
    toks_ngram <- quanteda::tokens_ngrams(tokens_from_example, n = 5:3)

@@

  all_tokens_with_errors <-
    all_tokens_with_errors %>%
    dplyr::mutate(tokens = stringr::str_replace_all(tokens, "_", " "),
                  first_words = stringr::word(tokens, start = 1, end = -2),
                  last_word = stringr::word(tokens, -1),
                  tokens = stringr::str_replace_all(tokens, " ", "_"),
                  first_words = stringr::str_replace_all(first_words, " ", "_"))

@@

  # Calculate the internal consistency score:
  internal_consistency <-
    internal_consistency %>%
    dplyr::ungroup()%>%
    dplyr::filter(!is.na(as_expected)) %>%
    dplyr::count(as_expected) %>%
    dplyr::mutate(consistency = true_count/sum(n))

@@

# Identify which words were unexpected
unexpected <-
  all_tokens_with_errors_only %>%
  dplyr::mutate(as_expected = last_word == last_word_expected) %>%
  dplyr::filter(as_expected == FALSE) %>%
  dplyr::select(-tokens)
}
```

@@

## $`internal consistency`
## # A tibble: 1 x 3
##   as_expected     n consistency
##   <lgl>       <int>       <dbl>
## 1 FALSE           1           0

## $`unexpected words`
## # A tibble: 1 x 3
##   first_words last_word last_word_expected 
##   <chr>       <chr>     <chr>                 
## 1 there_was   na        no

```

@@

## aRianna::generate_external_consistency_score(text_to_evaluate)
## $`external consistency`
## # A tibble: 1 x 3
##   as_expected     n consistency
##   <lgl>       <int>       <dbl>
## 1 FALSE           2       0.333
## 2 TRUE            1       0.333

>>>>

  # Create ngrams from the tokens
  toks_ngram <- 
    quanteda::tokens_ngrams(tokens_from_example, n = 5:3)

@@

  all_tokens_with_errors <-
    all_tokens_with_errors %>%
    dplyr::mutate(ngram = sapply(strsplit(tokens, "_"), length),
                  tokens = stringr::str_replace_all(tokens, "_", " "),
                  first_words = stringr::word(tokens, start = 1, end = -2),
                  last_word = stringr::word(tokens, -1),
                  tokens = stringr::str_replace_all(tokens, " ", "_"),
                  first_words = stringr::str_replace_all(first_words, " ", "_"))

@@

  # Calculate the internal consistency score:
  false_count <- length(internal_consistency[which(internal_consistency$as_expected == FALSE & 
                                                   internal_consistency$ngram == 3)])
  word_count <- sapply(strsplit(text_to_check, " "), length)
  true_count <- word_count - false_count

  internal_consistency <- tibble::tibble(
    "as_expected" = true_count,
    "unexpected"  = false_count,
    "consistency" = true_count/word_count
  )

@@

# Identify which words were unexpected
  unexpected <-
    all_tokens_with_errors_only %>%
    dplyr::mutate(as_expected = last_word == last_word_expected) %>%
    dplyr::filter(as_expected == FALSE) %>%
    dplyr::select(-tokens, -ngram, -as_expected)
}
```

@@

## $`internal consistency`
##   as_expected unexpected consistency
## 1           4          1         0.8

## $`unexpected words`
## # A tibble: 1 x 3
##   first_words last_word last_word_expected 
##   <chr>       <chr>     <chr>                 
## 1 there_was   na        no                 
```

@@

## aRianna::generate_external_consistency_score(text_to_evaluate)
## $`external consistency`
## # A tibble: 1 x 3
##   as_expected unexpected consistency
##         <int>      <int>       <dbl>
## 1           3          1        0.75
